---
format: dashboard
orientation: columns
---


## Col {width=20%}

::: {.card title="How to read this map?"}

This map organizes the tools from the Epiverse ecosystem based on the authors who created them.

Tools created by the same set of authors will be close to one another, while tools from completely unrelated groups will be far away.

Tools developed by authors who did not contribute to any other tools are dropped from this visualisation.

It can help users to find tools from development teams they already trust, or development teams using an approach that they like.

:::


## Col

```{r, cache = T}
ctv_pkgs <- jsonlite::fromJSON("https://epiverse-connect.r-universe.dev/api/packages/")

authors_edgelist <- ctv_pkgs |>
  dplyr::mutate(
    parsed_authors_r = purrr::map(authoritative::parse_authors_r(`Authors@R`), format, include = c("given", "family")),
    parsed_authors = authoritative::parse_authors(Author),
    .keep = "unused"
  ) |>
  dplyr::mutate(
    auts = dplyr::coalesce(parsed_authors, parsed_authors_r),
    auts = purrr::map(auts, stringi::stri_trans_general, "ASCII"),
    auts = purrr::map(auts, stringr::str_replace_all, "[[:punct:]]", " "),
    auts = purrr::map(auts, stringr::str_replace_all, "[[:space:]]+", " "),
    auts = purrr::map(auts, stringr::str_remove_all, "\\b(User|Developer)\\b"),
    auts = purrr::map(auts, trimws),
    .keep = "unused"
  ) |>
  tidyr::unnest_longer(auts) |>
  dplyr::mutate(auts = authoritative::expand_names(auts, auts)) |>
  # Standardize capitalization
  dplyr::mutate(
    auts = stringr::str_to_title(auts)
  ) |>
  dplyr::mutate(auts = dplyr::case_when(
    auts == "Lozano Jose E" ~ "Jose Lozano Alonso",
    auts == "Kevis Weiss" ~ "Kevin Weiss",
    auts == "Ahmad family = Rabiee" ~ "Ahmad Rabiee",
    auts == "Ed Ionides" ~ "Edward Ionides",
    TRUE ~ auts
  )) |>
  dplyr::select(Package, auts)
```

```{r}
aut_pkg_matrix <- authors_edgelist |>
  dplyr::mutate(placeholder = 1) |>
  tidyr::pivot_wider(names_from = auts, values_from = placeholder, values_fill = 0) |>
  tibble::column_to_rownames("Package")
```

```{r}
pkg_dist_from_auts <- aut_pkg_matrix |>
  dist(method = "binary") |>
  as.matrix()

# Drop pkgs that have 0 authors in common with any other
pkg_dist_no_overlap <- pkg_dist_from_auts[
  colSums(pkg_dist_from_auts) < nrow(pkg_dist_from_auts) - 1,
  rowSums(pkg_dist_from_auts) < ncol(pkg_dist_from_auts) - 1
]

pkg_dist <- pkg_dist_no_overlap |>
  cmdscale() |>
  as.data.frame() |>
  setNames(paste0("coord", 1:2)) |>
  tibble::rownames_to_column("package")
```

```{r}
library(ggplot2)

pkg_dist |>
  ggplot(aes(x = coord1, y = coord2, label = package)) +
    geom_point() +
    theme_void() +
    ggrepel::geom_text_repel()
```
