---
format: dashboard
orientation: columns
execute:
  echo: false
---

## Col {width=20%}

::: {.card title="How to read this map?"}

This map organizes the tools from the Epiverse ecosystem based on the scientific topic they focus on.

Tools focusing on similar scientific topics will be close to one another, while tools about completely unrelated topics will be far away.

It can help users to find tools related to their area of interest by looking at neighbours of tools that they are already using.

:::

## Col

```{text}
#| eval: false
#| echo: false
import torch
import pandas as pd

embeddings = torch.load("data/corpus_embeddings.pth")

pd.DataFrame(embeddings).to_csv("embeddings.csv", index = False)
```

```{r}
embeddings <- read.csv("data/embeddings.csv")
pkg_docs <- read.csv("data/analysis_df.csv")
```

```{r}
library(dplyr)
pkg_level_embeddings <- pkg_docs |>
    distinct(package_name, cluster_id) |>
    cbind(embeddings) |>
    group_by(package_name) |>
    summarize(across(starts_with("X"), median)) |>
    ungroup() |>
    tibble::column_to_rownames("package_name")
```

```{r}
pca_embeddings <- prcomp(pkg_level_embeddings, scale. = TRUE)
```

```{r}
library(ggplot2)
library(ggfortify)
autoplot(pca_embeddings) +
  theme_void() +
  ggrepel::geom_text_repel(aes(label = unique(pkg_docs$package_name)))
```